Draft Exploratory Analysis

### 2024-11-07 Data_Cleaning_20241031.Rmd
Final Version of Draft Exploratory Analysis
Fixed Y label for license over time graph

#Load Habitats:
habitats = raster("C:/Users/kdfro/Documents/MSU/GitHub/ECNS-560-Term-Project/Data/USGS Bison Habitat Map/mBISOx_CONUS_HabMap_2001v1/mBISOx_CONUS_HabMap_2001v1.tif")

>>>>

#Load Habitats:
#habitats = raster("C:/Users/kdfro/Documents/MSU/GitHub/ECNS-560-Term-Project/Data/USGS Bison Habitat Map/mBISOx_CONUS_HabMap_2001v1/mBISOx_CONUS_HabMap_2001v1.tif")

### 2024-11-07 Draft Exploratory Analysis.Rmd
Final Version of Draft Exploratory Analysis
Fixed Y label for license over time graph

  Once we confirmed that population is indeed declining, we started exploring fluctuations in hunting license numbers as a possible correlate. The following graph shows the number of hunting licenses across the same years and the same states as our previous visual:
![Great Plains Hunting License Numbers Over Time - Overall Trend](C:/Users/kdfro/Documents/MSU/GitHub/ECNS-560-Term-Project/Visuals/Hunting Licenses Over Time.png)

>>>>

  Once we confirmed that population is indeed declining, we started exploring fluctuations in hunting license numbers as a possible correlate. The following graph shows the number of hunting licenses across the same years and the same states as our previous visual:
![Great Plains Hunting License Numbers Over Time - Overall Trend](C:/Users/kdfro/Documents/MSU/GitHub/ECNS-560-Term-Project/Visuals/Licenses Over Time Fixed.png)
